Millions of Type Errors

### 2023-08-02 programming23/paper.tex
rm cleveref, its in programming.sty
data review

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

@@

\begin{itemize}
  \item
    Collect metrics instead of source code: lines, modules, num errors
  \item
    Track an edit range to compare type errors with edits,
    use a coarse $[min, max]$ interval for speed
  \item
    Count specific errors only for the current edit range
    (reduces size of logs)
  \item
    Log randomly on keystroke instead of per specific event.
    One exception: log module switches because that helps discover
    codebases that use several analysis modes.
    Randomness helps lower the amount of data.
  \item
    Observe sessions randomly (again to lower the amount of data).
\end{itemize}

@@

  \begin{tabular}{l@{~}cccccc}
    &             & PII       & Session ID & Deterministic & Private Data \\\midrule
    & Transparent & \chkNo    & \chkNo     & \chkYes       & \chkNo      \\
  * & Lite        & \chkNo    & \chkYes    & \chkNo        & \chkYes     \\
    & \code{.NET} & \chkMaybe & \chkYes    & \chkYes       & \chkYes     \\
    & VS Code     & \chkYes   & \chkYes    & \chkYes       & \chkYes     \\
  \end{tabular}
\end{table}

>>>>

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

Prior work: transparent telemetry, VS Code telemetry, many others undocumented
that are probably not cleary documented.
\Cref{t:telemetry-design} gives an overview.

@@

\begin{itemize}
  \item
    Collect metrics instead of source code: lines, modules, num errors
  \item
    Track an edit range to compare type errors with edits,
    use a coarse $[min, max]$ interval for speed
  \item
    Count specific errors only for the current edit range
    (reduces size of logs)
  \item
    Within the edit range, collect data before and after the latest edits.
  \item
    Log randomly on keystroke instead of per specific event.
    One exception: log module switches because that helps discover
    codebases that use several analysis modes.
    Randomness helps lower the amount of data.
  \item
    Observe sessions randomly (again to lower the amount of data).
\end{itemize}

@@

  \begin{tabular}{l@{~}cccccc}
    &             & PII       & Session ID & Deterministic & Private Data \\\midrule
    & Transparent & \chkNo    & \chkNo     & \chkYes       & \chkNo      \\
  * & Us          & \chkNo    & \chkYes    & \chkNo        & \chkYes     \\
    & \code{.NET} & \chkMaybe & \chkYes    & \chkYes       & \chkYes     \\
    & VS Code     & \chkYes   & \chkYes    & \chkYes       & \chkYes     \\
  \end{tabular}
\end{table}
